---
title: "NYC AirBnb Report"
author: "Nouhaila Astif"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


> Plan 

* The question
* code:
   + Data exploration and cleaning
   + Data visualization
   + Data mining 



```{r libraries,echo=FALSE, message=FALSE,warning=FALSE}
library(plyr)
library(dplyr)
library(tidyr)
library(leaflet)
library(tidytext)
library(widyr)
library(ggplot2)
library(igraph)
library(ggraph)
library(stringr)
library(wesanderson)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
```


```{r, loading_data, echo=FALSE}
data <- read.csv("AB_NYC_2019.csv")
```


## Question 

> What factor affects more the price of the AirBnb in NYC 

## Our Analysis


```{r}
length(data)
```
```{r}
nrow(data)
```

```{r}
colnames(data)
```
```{r}
summary(data$price)
```

## Cleaning data

> we will try to find the names of columns which contain missing values

```{r}
colnames(data)[colSums(is.na(data)) > 0]
```
> then replacing the null reviews to 0

```{r}
data$reviews_per_month[is.na(data$reviews_per_month)] <- 0
```
> checking 

```{r}
colnames(data)[colSums(is.na(data)) > 0]
```

> subsetting the columns we find relevant, for that we're going to dropsome columns

```{r}
drop <- c("id","last_review","host_name")
nyc <- data[,!(names(data)%in%drop)]
```

## Data Visualization

> first let's plot the prominent descriptive data in our data set

* Manhattan

```{r}
# since we cannot plot the almost 50K adress, we're going to plot only 20 adress from two cities as a sample

manhattan <- nyc[nyc$neighbourhood_group == "Manhattan",] %>% head(20)
```


```{r, warning=FALSE,message=FALSE}
leaf_manhattan <-manhattan %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(popup = manhattan$neighbourhood_group)
leaf_manhattan
```

* Brooklyn
```{r, message=FALSE, warning=FALSE}
brooklyn <- nyc[nyc$neighbourhood_group == "Brooklyn",] %>% head(20)

leaf_br <-brooklyn %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(popup = brooklyn$neighbourhood_group)
leaf_br
```

> graphs about price 

```{r,warning=FALSE, message=FALSE}
# Filtering on price

b<-nyc %>% select(price) %>% filter(price<=5000)

ggplot(b, aes(x=price)) + 
    geom_histogram(alpha=0.9,fill="lightsalmon4") +theme_minimal() +
    ggtitle("The distribution of price") + labs(x="Price")


```


```{r}
# transforming price to log since it's a highly skewed variable to a have a more normalized data

table<-aggregate(log(nyc$price + 1),list(nyc$neighbourhood_group,nyc$room_type), mean)

```


```{r}
# Determine the palette we want to use in the 
Color <- wes_palette("GrandBudapest1", n= 5, type= "continuous")
ggplot(table, aes(factor(Group.2), x, fill = Group.1)) + 
  geom_bar(stat="identity", position = "dodge") + 
  scale_fill_manual(breaks = c("Bronx", "Brooklyn", "Manhattan","Queens","Staten Island"), 
                       values = Color)+theme_minimal() +
                      labs(x="",y='Log of price',fill="Neighbourhood")
```


```{r}
homes <- nyc[nyc$room_type =="Entire home/apt" ,]

homes_log<-aggregate(log(homes$price), list(homes$neighbourhood,homes$neighbourhood_group), mean)
homes_log<-homes_log %>% arrange(desc(x))


```

```{r}
ggplot(homes_log[1:10,], aes(reorder(Group.1,-x), x, fill = Group.2)) + 
    geom_bar(stat="identity", position = "dodge") + 
    theme(axis.text.x=element_blank()) + ggtitle("Best 10 neighborhoods") +
    xlab("Neighborhood") +
    ylab("Log-price") + ylim(0,8) +
    labs(fill="Neighborhood")+
    scale_fill_manual(breaks = c("Bronx", "Brooklyn", "Manhattan","Queens","Staten Island"), 
                       values=Color)

```

## Data wrangling and Mining part 

```{r}
# tidying the data 
Names <- tibble(Id = nyc$host_id,
                Name=nyc$name) %>% 
  unnest(Name)
Names
```


```{r, message= FALSE, warning=FALSE}
#token word

Names1 <- mutate(Names, name= as.character(Names$Name))

Names1 <- Names1 %>% unnest_tokens(word, name) %>% anti_join(stop_words)
Names1 <-Names1 %>% select("Id","word")
Names1
```

```{r}
Names <- Names1 %>% count(word, sort=TRUE)
Names
```

```{r}
set.seed(1234)
wordcloud(words = Names1$word, freq = Names$n, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.50, 
          colors=brewer.pal(8, "Dark2"))
```

